\ttitle

### 2015-06-23 Chapters/CPET_Survival.tex
Kaplan-Meier, Cox Regression - tumour factors
- Complete and include KM plot
- Minor edits of all other tables
- Include new table on Cox regression incl tumour factors
- TODO - ?Split tables into uni and multi
- TODO - Fix tables spilling over margins

\input{Tables/cpet_survival_cox_regression}

@@

%UNIVARIATE Cox-regression analysis
The clinico-pathological characteristics of the patients studied (n=47) are shown in \ref{table:cpet_survival_cox} on p\pageref{table:cpet_survival_cox}. POSSUM Physiology score $>$14 (HR 2.38, 95\% CI 1.19 - 4.75, p = 0.014) and preoperative serum C-reactive protein $>$ 10 mg/dl (HR 2.14, 95\% CI 1.04 - 4.41, p = 0.04) were associated with survival on univariate Cox-regression analysis. Cardiopulmonary exercise test parameters including $\dot{V}_{O_2}$AT, $\dot{V}_{O_2}$Peak and $\dot{V}_E/\dot{V}_{CO_2}$ were not associated with survival on univariate analysis.
%MULTIVARIATE Cox-regression analysis
On multi-variate backward conditional regression analysis using POSSUM Physiology Score and serum C-reactive protein as independent variables, only POSSUM Physiology Score $>$14  was found to be an independent predictor of survival (HR 2.38, 95\% CI 1.19 - 4.75, p = 0.014).

@@

Cardiopulmonary exercise testing parameters in survivors and non-survivors at 6 months, 12 months and 24 months are shown in tables \ref{table:cpet_survival_6months}, \ref{table:cpet_survival_12months}, \ref{table:cpet_survival_24months}.

@@

>>>>

\input{Tables/cpet_survival_cox_regression}
\input{Tables/cpet_survival_cox_tumour_factors}

@@

%UNIVARIATE Cox-regression analysis
The clinico-pathological characteristics of the patients studied (n=47) are shown in \ref{table:cpet_survival_cox} on p\pageref{table:cpet_survival_cox}. POSSUM Physiology score $>$14 (HR 2.38, 95\% CI 1.19 - 4.75, p = 0.014) and preoperative serum C-reactive protein $>$ 10 mg/dl (HR 2.14, 95\% CI 1.04 - 4.41, p = 0.04) were associated with survival on univariate Cox-regression analysis. Cardiopulmonary exercise test parameters including $\dot{V}_{O_2}$AT, $\dot{V}_{O_2}$Peak and $\dot{V}_E/\dot{V}_{CO_2}$ were not associated with survival on univariate analysis.
%MULTIVARIATE Cox-regression analysis
On multi-variate backward conditional regression analysis using POSSUM Physiology Score and serum C-reactive protein as independent variables, only POSSUM Physiology Score $>14$  was found to be an independent predictor of survival (HR 2.38, 95\% CI 1.19 - 4.75, p = 0.014).

Kaplan-Meier survival analysis comparing survival in patients with a low ($leq14$) versus high ($>14$) POSSUM Phsyiology Score is shown in Fig. \ref{fig:cpet_survival_km_possum}. Estimated median survival was  32 months (95\% CI 17.02 - 46.99) in patients with a low POSSUM Physiology Score but reduced to 14 months (95\% CI 9.51 - 18.49) in a high POSSUM Physiology Score (p = 0.012).

%Figure 1
\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/cpet_survival_km_possum}
	\caption{Kaplan-Meier Survival Analysis of POSSUM Physiology Score ($\leq14$ vs. $>14$)}
	\label{fig:cpet_survival_km_possum}
\end{figure}

@@

Cardiopulmonary exercise testing parameters in survivors and non-survivors at 6 months, 12 months and 24 months are shown in tables \ref{table:cpet_survival_6months}, \ref{table:cpet_survival_12months}, \ref{table:cpet_survival_24months}. Load achieved at peak exercise was significantly higher in patients who survived at least 6 months (118.5 vs. 76.5 watts, p = 0.026) However, there was no association between any of the other cardiopulmonary exercise testing parameters and survival at 6 months, 12 months or 24 months.

@@

%Compare significant preoperative factors with tumour factors
